---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Anthony Coll"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_race, aes(x = date, y = White_count)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?

I wrote code that depicts the total count of cases of Covid in Pennsylvania and a separate code that depicts the total count of deaths due to Covid in Pennsylania during the same time frame.


```{r}
covid_data_race |>
  filter(count_type == "Cases", state == "PA") |>
  ggplot(aes(x = date, y = Total_count)) + geom_line(color = "red") + scale_x_date("Date") + scale_y_continuous("Total Cases")
```

```{r}
covid_data_race |>
  filter(count_type == "Deaths", state == "PA") |>
  ggplot(aes(x = date, y = Total_count)) + geom_line(color = "blue") + scale_x_date("Date") + scale_y_continuous("Total Deaths")
```


2. Are there any conclusions you can draw?

As expected, it seems as though total deaths generally lag behind total cases. For example, there seemed to be a spike in cases in December, which lead to a spike in deaths in January.

3. What were you not able to do due to not having the R knowledge?

It would be helpful to overlay the two graphs on top of one another in order to more easily the trend described in #2, which is something I do not yet know how to do.

4. What other data would be useful to better understand this data?

It would be helpful to compare this data to national trends to gauge Pennsylvania's response compared to the country as a whole.

